fdcoexist

### 2018-08-23 paper_simulations.Rmd
Plots of CWV against environment.

@@

@@

plot_trait_var_env_varying
```

>>>>

NB: When $i$ = $j$, the species faces intra-specific competition leading to:
$$\delta_{ii} = \frac{K}{(K - N{t,i,x})}$$

@@

cat('\r\n\r\n')

@@

plot_trait_var_env_varying

cat('\r\n\r\n')

```

# CWV against environment

```{r cwv_envt}

var_df %>%
    select(-contains("cwm")) %>%
    filter(compet_status == "no_compet") %>%
    gather("trait_name", "trait_value", contains("trait")) %>%
    group_by(compet_status, cor_level, scenario, patch, trait_name) %>%
    summarise(trait_cwv = Weighted.Desc.Stat::w.var(trait_value, mu = N)) %>%
    mutate(patch_optim = gsub("patches", "", patch) %>%
               as.numeric()) %>%
    ggplot(aes(patch_optim, trait_cwv, color = trait_name)) +
    geom_point() +
    geom_smooth(se = FALSE) +
    facet_grid(vars(cor_level), vars(scenario), scales = "free_y",
               labeller = labeller(scenario = label_value,
                                   cor_level = c(no_cor   = "r = 0",
                                                 low_cor  = "r = 0.3",
                                                 high_cor = "r = 0.7"))) +
    scale_color_discrete(labels = c(trait1_cwm = "Trait 1",
                                    trait2_cwm = "Trait 2",
                                    trait3_cwm = "Trait 3")) +
    labs(x = "Environment",
         y = "Community-Weighted Variance (CWV)",
         color = NULL,
         subtitle = paste0("Varying environment; ",
                           d * 100, "% dispersal;",
                           " No competition")) +
    theme(legend.position = "top")

cat('\r\n\r\n')

var_df %>%
    select(-contains("cwm")) %>%
    filter(compet_status == "compet") %>%
    gather("trait_name", "trait_value", contains("trait")) %>%
    group_by(compet_status, cor_level, scenario, patch, trait_name) %>%
    summarise(trait_cwv = Weighted.Desc.Stat::w.var(trait_value, mu = N)) %>%
    mutate(patch_optim = gsub("patches", "", patch) %>%
               as.numeric()) %>%
    ggplot(aes(patch_optim, trait_cwv, color = trait_name)) +
    geom_point() +
    geom_smooth(se = FALSE) +
    facet_grid(vars(cor_level), vars(scenario), scales = "free_y",
               labeller = labeller(scenario = label_value,
                                   cor_level = c(no_cor   = "r = 0",
                                                 low_cor  = "r = 0.3",
                                                 high_cor = "r = 0.7"))) +
    scale_color_discrete(labels = c(trait1_cwm = "Trait 1",
                                    trait2_cwm = "Trait 2",
                                    trait3_cwm = "Trait 3")) +
    labs(x = "Environment",
         y = "Community-Weighted Variance (CWV)",
         color = NULL,
         subtitle = paste0("Varying environment; ",
                           d * 100, "% dispersal;",
                           " Competition")) +
    theme(legend.position = "top")

```
